\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG

### 2017-02-17 paper.tex
fixed compiler error

In our analysis, some notable patterns emerged. First, the \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants. Classifiers overall distinguished the \textit{breathe}  and \texit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e. that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \texit{song}, for example. Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes). This short timespan is somewhat surprising, given that some tasks (like songs) presumably rely on changes or patterns over a longer period of time.

>>>>

In our analysis, some notable patterns emerged. First, the \textit{breathe},
\textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
Classifiers overall distinguished the \textit{breathe}  and \textit{listen} tasks even compared
to the same tasks from other participants, implying that these tasks are expressed differently
for each participant, i.e. that they have an inherence factor sufficient for authentication,
even though they task do not involve an explicit secondary knowledge factor as in \textit{sport}
or \textit{song}, for example. Second, we were able to achieve good results by generating feature
vectors based on only 500ms (300 voltage readings across the three electrodes).
This short timespan is somewhat surprising, given that some tasks (like songs)
presumably rely on changes or patterns over a longer period of time.
